Smart Model Elimination for Efficient Automated Machine Learning in Healthcare

### 2024-06-24 paper/paper.tex
feature importance

When a user inputs a dataset into SMEML, it first extracts the attributes from the dataset. It feeds these attributes into the boosting model to get the predicted rank of each model. Since we have determined that we can predict a top two model within the predicted top eight quite confidently, we can eliminate the bottom 18 models from the list. We run Bayseian optimization on the top eight models to get the best hyperparamters for each model. We select the top models that have significantly better performance than other models. These models are stacked together to form the final model. This process is shown in Figure 1.
\begin{table}
  \caption{Attributes extracted from a dataset}
  \label{model-options-table}
  \centering
  \begin{tabular}{lll}
    \toprule
    Attribute & Formula & Purpose\\
    \midrule
    \# of Rows & $|\mathbf{A}|_r$ & Data Size \\
    \hline
    \# of Columns & $|\mathbf{A}|_c$ & Data Size \\
    \hline
    Target Distribution &
    $\frac{\max(\text{count}_1, \text{count}_0)}{|\mathbf{A}|_r}$
    & Data Type \\
    \hline
    Numerical Columns &
    $\frac{|\mathbf{A}_{num}|}{|\mathbf{A}|_{c}}$
    & Data Type \\
    \hline
    Binary Categorical Columns &
    $\frac{|\mathbf{A}_{bin}|}{|\mathbf{A}|_{c}}$
    & Data Type \\
    \hline
    Mean \# of Distinct Values  & $\mu \left\{\text{\# of distinct values in column}\right\}$ & Data Type \\ 
    \hline
    Mean IQR  & $\mu \left\{\text{IQR of column}\right\}$ & Data Distribution \\ 
    \hline
    STD of IQR  & $\sigma \left\{\text{IQR of column}\right\}$ & Data Distribution \\
    \hline
    Mean Q1 & $\mu \left\{\text{Q1 of column}\right\}$ & Data Distribution \\
    \hline
    STD of Q1  & $\sigma \left\{\text{Q1 of column}\right\}$ & Data Distribution \\
    \hline
    Mean Q3  & $\mu \left\{\text{Q3 of column}\right\}$ & Data Distribution \\
    \hline
    STD of Q3  & $\sigma \left\{\text{Q3 of column}\right\}$ & Data Distribution \\
    \hline
    Mean Percent of Z-Score Outliers  & 
    $\mu \left\{ \frac{\text{\# of Z-Score Outliers}}{|\mathbf{A}|_r} \right\}$ & Outlier Data Points \\
    \hline
    STD of Percent of Z-Score Outliers  &
    $\sigma \left\{ \frac{\text{\# of Z-Score Outliers}}{|\mathbf{A}|_r} \right\}$ & Outlier Data Points \\
    \hline
    Mean Correlation& $\mu \left\{\text{Correlation Matrix}\right\}$ & Data linearity \\
    \hline
    STD of Correlation & $\sigma \left\{\text{Correlation Matrix}\right\}$ & Data Linearity \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

When a user inputs a dataset into SMEML, it first extracts the attributes from the dataset. It feeds these attributes into the boosting model to get the predicted rank of each model. Since we have determined that we can predict a top two model within the predicted top eight quite confidently, we can eliminate the bottom 18 models from the list. We run Bayseian optimization on the top eight models to get the best hyperparamters for each model. We select the top models that have significantly better performance than other models. These models are stacked together to form the final model. This process is shown in Figure 1.
\begin{table}
  \caption{Attributes extracted from a dataset}
  \label{model-options-table}
  \centering
  \begin{tabular}{llll}
    \toprule
    Attribute & Formula & Purpose & Weight\\
    \midrule
    \# of Rows & $|\mathbf{A}|_r$ & DS & .0422 \\
    \hline
    \# of Columns & $|\mathbf{A}|_c$ & DS & .0415 \\
    \hline
    Target Distribution &
    $\frac{\max(\text{count}_1, \text{count}_0)}{|\mathbf{A}|_r}$
    & DT & .0489 \\
    \hline
    Numerical Columns &
    $\frac{|\mathbf{A}_{num}|}{|\mathbf{A}|_{c}}$
    & DT & .0428 \\
    \hline
    Binary Categorical Columns &
    $\frac{|\mathbf{A}_{bin}|}{|\mathbf{A}|_{c}}$
    & DT & .0117 \\
    \hline
    Mean \# of Distinct Values  & $\mu \left\{\text{\# of distinct values in column}\right\}$ & DT & .0076 \\ 
    \hline
    Mean IQR  & $\mu \left\{\text{IQR of column}\right\}$ & DD & .0594 \\ 
    \hline
    STD of IQR  & $\sigma \left\{\text{IQR of column}\right\}$ & DD & .0700 \\
    \hline
    Mean Q1 & $\mu \left\{\text{Q1 of column}\right\}$ & DD & .0789 \\
    \hline
    STD of Q1  & $\sigma \left\{\text{Q1 of column}\right\}$ & DD & .0613 \\
    \hline
    Mean Q3  & $\mu \left\{\text{Q3 of column}\right\}$ & DD & .0812 \\
    \hline
    STD of Q3  & $\sigma \left\{\text{Q3 of column}\right\}$ & DD & .1103 \\
    \hline
    Mean Percent of Z-Score Outliers  & 
    $\mu \left\{ \frac{\text{\# of Z-Score Outliers}}{|\mathbf{A}|_r} \right\}$ & ODP & .0558 \\
    \hline
    STD of Percent of Z-Score Outliers  &
    $\sigma \left\{ \frac{\text{\# of Z-Score Outliers}}{|\mathbf{A}|_r} \right\}$ & ODP & .0798 \\
    \hline
    Mean Correlation& $\mu \left\{\text{Correlation Matrix}\right\}$ & DL & .0559 \\
    \hline
    STD of Correlation & $\sigma \left\{\text{Correlation Matrix}\right\}$ & DL & .1526 \\
    \bottomrule
  \end{tabular}
  \captionsetup{font=footnotesize}
  \caption*{\textbf{Abbreviations}: DS: Data Size, DT: Data Type, DD: Data Distribution, ODP: Outlier Data Points, DL: Data Linearity}
\end{table}
